% TODO: ADD DOE SCGSR?
This work represents an amalgamation of six years of my life. Looking back on those six years, I've fundamentally changed in so many ways. I experienced memories that will last a lifetime, and tough times that I could not have made it through without a network of friends and family behind me. Thank you all for your guidance, your friendship, and your support.

First, I'd like to thank my advisor, Jahred Adelman. Your guidance has made me into the scientist I am today. I walked into this knowing very little about research, and your patience and wisdom shaped how I approach problems and my understanding of physics. I cannot thank you enough for the time you've poured into me and the places you've led me.

Next I'd like to thank Liza Brost, your mentorship was absolutely vital to my growth. The time you invested into me and care toward my success led me to be able to reach this point, and I cannot thank you enough for that. Beyond research, I could not have thrived at CERN without you, and I'm incredibly thankful for the support and guidance you provided in that chapter of my life.

Countless other scientists who have contributed to my growth and development. Specifically, I'd like to thank Jeremy Love, for the considerable guidance since the start of my time on ATLAS. I want to thank Walter Hopkins, for the countless conversations about physics and machine learning on the way to the coffee machine, and knowledge and insight that brought me. Beyond that, I'd like to thank the many other scientists I've been able to look up to along the way, for your mentoring and for the example you provided: Max Swiatlowski, Jonathan Long, Tova Holmes, Kate Whalen, Christopher Meyer, amongst many others.

I'd like to thank my friends who supported me during my time at CERN: John Myers, Lesya Horyn, Todd Seiss, Rob Mina, Elliot Parrish, Bingxuan Liu. Moving to the other side of the world was absolutely daunting, but you all made it an experience I won't ever forget. Also, thank you to Luca Buonocore, Francesca Forte, Roberto Cevenini, Gianmarco Pompeo, and Francesco Riccardi. When I moved into our apartment in Saint-Genis, I knew I'd found a place to live, but I didn't realize the Italian family I would inherit while there. 

Pawel Klimek, Blake Burghgrave, Puja Saha, Brianna Stamas, Louis D'Eramo, and Dhiman Chakraborty thank you for contributing your thoughts, ideas, and input to my work. Also, thank you to all of the professors at NIU who taught me in a class or influenced me along the way, specifically Michael Eads and Stephen Martin. I could not have survived through classes, finals, and candidacy exams without the support of many other NIU graduate students, especially Mike McEvoy, Alex Halavanau, Marc Pavlik, Dan Faia, Andrew Fiedler, and Daniel Stange. 

To the friends who have seen me grow up, who have been there from the beginning, and who have stuck through life with me, thank you. Aaron and Erin Spargur, Todd and Alex Grumley, Jacob Kreeb, Michael Hoelscher, and Lauren Ruser, being around you all has always felt like home, and having that throughout this chapter of my life was essential. Grant Knox, thank you for always being someone I could talk to about anything. Additionally to the many other friends who have spent time with me throughout the course of this degree, thank you, I could not have made it without the mental rest your friendship provided: John Mueth, Brendan Nelson, Joe Rossi, Naaim Siddiqi, and many others.

I'd like to thank Mike Rogier, the first instructor who made me excited about physics. All journeys have a start, and this is one that started in your classroom. I'm thankful for the spirit you brought to teaching, and to the confidence you showed in me. 

Last, thank you to my family. Getting to this point has been an adventure. One that has taken me far and wide, and one that has taken me through highs and lows. Dad and Mom, thank you for being there with me through it all. Thank you for developing me into the man I am today. Colin, Aralynn, and Owen -- one of the toughest sacrifices of this degree has been having to watch you grow up from afar. I'm excited to see who you all grow up to be and hope that, in some shape, this inspires you to pursue your passions.
\\

\quoteAuthor{The beautiful thing about learning is nobody can take it away from you.}{B.B. King}

